Equalizer: A Mature Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Compound configs
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@21 db7c848b-7755-4df2-b763-8796797afa52

\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{times}
%\usepackage{tabularx}
\usepackage{amsmath}
%\usepackage{url}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{paralist}

@@

The initial version of Equalizer implemented sort-first (2D), sort-last (DB),
stereo (EYE) and multilevel decompositions \cite{EMP:09}. In the following we present new
decomposition modes and motivate their use case. \fig{fig:compounds} provides an
overview of the new modes.

\begin{figure*}[ht]\center
  \subfigure[Time-Multiplex]{\label{fig:dplex}
    \includegraphics[width=0.24\textwidth]{images/dplex}}\hfil
  \subfigure[Tiles]{\label{fig:tile}
    \includegraphics[width=0.24\textwidth]{images/tile}}\hfil
  \subfigure[Pixel]{\label{fig:pixel}
    \includegraphics[width=0.24\textwidth]{images/pixel}}\hfil
  \subfigure[Subpixel]{\label{fig:subpixel}
    \includegraphics[width=0.24\textwidth]{images/subpixel}}\hfil
  \caption{New Equalizer task decompositions for parallel rendering}
  \label{fig:compounds}
\end{figure*}

@@

Time-multiplexing (\fig{fig:dplex}), or DPlex, was implemented in \cite{BRE:05}
for shared memory machines. It is however a better fit for distributed memory
systems, since the separate memory space makes concurrent rendering of different
frames easier to implement. While it increases the framerate linearly, it does
not decrease the latency between user input and the corresponding
output. Consequently, this decomposition mode is mostly useful for
non-interactive movie generation. It is transparent to Equalizer applications,
but does require the configuration latency to be equal or greater than the
number of source channels. Furthermore, to work in a multi-threaded, multi-GPU
configuration, the application needs to support running the rendering threads
asynchronously, as outlined in \sref{SEC_threading}. The output frame rate of
the destination channel is smoothened using a frame rate equalizer
(\sref{SEC_framerateEq}).

@@

\begin{figure*}[ht]\center
  \subfigure[Load-Balancing]{\label{fig:loadeq}
    \includegraphics[width=0.24\textwidth]{images/loadeq}}\hfil
  \subfigure[Cross-Segment Load-Balancing]{\label{fig:vieweq}
    \includegraphics[width=0.24\textwidth]{images/vieweq}}\hfil
  \subfigure[Dynamic Frame Resolution]{\label{fig:dfr}
    \includegraphics[width=0.24\textwidth]{images/dfr}}\hfil
  \subfigure[Monitoring]{\label{fig:monitor}
    \includegraphics[width=0.24\textwidth]{images/monitoreq}}\hfil
  \caption{Runtime modifications}
  \label{fig:equalizers}
\end{figure*}

>>>>

\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{times}
%\usepackage{tabularx}
\usepackage{amsmath}
%\usepackage{url}
\usepackage{caption,subcaption}
\usepackage{multirow}
\usepackage{paralist}
\usepackage{listings}

@@

The initial version of Equalizer implemented sort-first (2D), sort-last (DB),
stereo (EYE) and multilevel decompositions \cite{EMP:09}. In the following we
present new decomposition modes and motivate their use case. \fig{fig:compounds}
provides an overview of the new modes. We describe their configuration in
same \textit{compound} framework introduced in \cite{EMP:09}

\begin{figure*}[ht]\center
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{images/dplex}
      \caption{\label{fig:dplex}Time-Multiplex}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{images/tile}
      \caption{\label{fig:tile}Tiles}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{images/pixel}
      \caption{\label{fig:pixel}Pixel}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{images/subpixel}
      \caption{\label{fig:subpixel}Subpixel}
  \end{subfigure}
  \caption{New Equalizer task decompositions for parallel rendering}
  \label{fig:compounds}
\end{figure*}

@@

Time-multiplexing (\fig{fig:dplex}), also called AFR or DPlex, was first
implemented in \cite{BRE:05} for shared memory machines. It is however a better
fit for distributed memory systems, since the separate memory space makes
concurrent rendering of different frames easier to implement. While it increases
the framerate linearly, it does not decrease the latency between user input and
the corresponding output. Consequently, this decomposition mode is mostly useful
for non-interactive movie generation. It is transparent to Equalizer
applications, but does require the configuration latency to be equal or greater
than the number of source channels. Furthermore, to work in a multi-threaded,
multi-GPU configuration, the application needs to support running the rendering
threads asynchronously, as outlined in \sref{SEC_threading}. The output frame
rate of the destination channel is smoothened using a frame rate equalizer
(\sref{SEC_framerateEq}).

\begin{figure*}[ht]\center
  \begin{subfigure}[b]{0.24\textwidth}
    {\tiny\begin{lstlisting}
compound {
  channel "destination"
  framerate_equalizer {}
  compound {
    channel "source1"
    phase 0 period 2
    outputframe  { name "frame" }
  }
  compound {
    channel "source2"
    phase 1 period 2
    outputframe  { name "frame" }
  }
  inputframe { name "frame" }
}
    \end{lstlisting}}
    \caption{\label{eqc:dplex}Time-Multiplex}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    {\tiny\begin{lstlisting}
compound {
  channel "destination"
  outputtiles {
    name "queue"
    size [ 64 64 ]
  }
  compound {
    channel "destination"
    inputtiles { name "queue" }
  }
  compound {
    channel "source"
    inputtiles { name "queue" }
    outputframe {}
  }
  inputframe { name "frame.source" }
}
    \end{lstlisting}}
    \caption{\label{eqc:tiles}Tiles}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    {\tiny\begin{lstlisting}
compound {
  channel "dest"
  compound {
    channel "dest"
    pixel [ 0 0 2 1 ]
    outputframe { type texture }
  }
  compound {
    channel "source"
    pixel [ 1 0 2 1 ]
    outputframe{}
  }
  inputframe { name "frame.dest" }
  inputframe { name "frame.source" }
}
    \end{lstlisting}}
    \caption{\label{eqc:pixel}Pixel}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    {\tiny\begin{lstlisting}
compound {
  channel "dest"
  compound {
    channel "dest"
    subpixel [ 0 2 ]
    outputframe { type texture }
  }
  compound {
    channel "source"
    subpixel [ 1 2 ]
    outputframe{}
  }
  inputframe { name "frame.dest" }
  inputframe { name "frame.source" }
}
    \end{lstlisting}}
    \caption{\label{eqc:subpixel}Subpixel}
  \end{subfigure}
  \caption{Compound configurations for \fig{fig:compounds}}
  \label{eqc:compounds}
\end{figure*}

@@

\begin{figure*}[ht]\center
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{images/loadeq}
      \caption{\label{fig:loadeq}Load-Balancing}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{images/vieweq}
      \caption{\label{fig:vieweq}Cross-Segment Load-Balancing}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{images/dfr}
      \caption{\label{fig:dfr}Dynamic Frame Resolution}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{images/monitoreq}
      \caption{\label{fig:monitor}Monitoring}
  \end{subfigure}
  \caption{Runtime modifications}
  \label{fig:equalizers}
\end{figure*}
